On the effects of partying on next-day sports performance

### 2017-07-12 writing/draft.tex
Added note on how further research might investigate how the hangover effect tapers as a function of time.

\paragraph{General}
In both sports, it's possible there are prolonged effects of partying, and applying some sort of kernel on the number of hours played since the last game could be interesting; recall that our decision to only look at back-to-back games 
within 24 hours of each other was only motivated by intuition and not guided by data. 
Future work may consider similar effects in European soccer leagues.

>>>>

\paragraph{General}
In both sports, it's possible there are prolonged effects of partying, and applying some sort of kernel on the number of hours played since the last game could be interesting; recall that our decision to only look at back-to-back games 
within 24 hours of each other was only motivated by intuition and not guided by data; How does the effect taper off as a function of time? 
Future work may consider similar effects in NHL or European soccer leagues.
